Titeln på avhandlingens språk

### 2022-11-03 implications_optimization.tex
sampling

\begin{figure}
    \centering
    \begin{subfigure}[]{\columnwidth}
        \centering
        \includegraphics[width=\textwidth]{figs/new_model/lifetime_all_ttfs.png}
        \caption{%
            Evolution of mean application lifetimes as \acp{TTF} increase.
            Error bars indicate \SI{95}{\percent} \acp{CI}.
        }
    \end{subfigure}
    \begin{subfigure}[]{\columnwidth}
        \centering
        \includegraphics[width=\textwidth]{figs/new_model/lifetime_diff.png}
        \caption{%
            Percentage difference in mean application lifetimes with respect to the reference model at select \acp{TTF}.
            Error bars indicate the \SI{95}{\percent} \acp{CI}, calculated using a two-sample T-test.
        }
    \end{subfigure}
    \caption{\acl{TTF} versus application lifetime.}\label{fig:lifetimes}
\end{figure}

@@

We proceed to set up an experiment where these sampling scheme variants are deployed on identical, simulated, \num{100}-step tasks.
Also included for reference in this experiment is greedy (also known as \emph{zero-wait}) sampling, where samples are taken as fast as possible; a new sample is taken as soon as the result for the previous one has been received.
This is the default sampling strategy used in most existing \ac{WCA} prototypes.
The execution times for each step are generated by a realistic model parameterized with high neuroticism and without any distribution fitting on the data (this timing model is separate from the internal timing models inside the sampling schemes).
We set \( R_\text{min} \) to \SI{0.5}{\hertz}, \( \alpha \) to \num{3.0}, and the \ac{RTT} of the system to a constant \SI{150}{\milli\second}, and then run \num{90} repetitions of the task for the original design of the sampling scheme as well as for each possible configuration of it with a different parameterization of the timing model.

\begin{figure}
    \centering
    \begin{subtable}[]{\columnwidth}
        \centering
        \begin{tabular}{rrr}
            \toprule
            \( R_\text{min} \) & \( \alpha \) & \ac{RTT} \\
            \midrule
            \SI{0.5}{\hertz} & \num{3.0} & \SI{150}{\milli\second} \\
            \bottomrule
        \end{tabular}
        \caption{Parameters used for \textcite{Wang2019Towards}'s adaptive sampling scheme.}
    \end{subtable}
    \begin{subfigure}[]{\columnwidth}
        \centering
        \includegraphics[width=\textwidth]{figs/new_model/sampling_junjue.png}
        \caption{%
            Mean number of samples per step over a \num{100}-step task, \num{90} independent repetitions per configuration.
            Error bars indicate \SI{95}{\percent} \acp{CI}.
        }
    \end{subfigure}
    \begin{subfigure}[]{\columnwidth}
        \centering
        \includegraphics[width=\textwidth]{figs/new_model/diff_sampling_junjue.png}
        \caption{%
            Percentage difference in mean number of samples per step.
            Error bars indicate the \SI{95}{\percent} \acp{CI}, calculated using a two-sample T-test.
            \todo[inline]{%
                Add greedy.
                Develop optimal sampling scheme?
                Explain grouping better?
            }
        }
    \end{subfigure}
    \caption{%
        Results of parameterizing \textcite{Wang2019Towards}'s adaptive sampling scheme using the realistic timing model.
        \emph{ED2} indicates a sampling scheme using the \edgedroid{} model for \ac{CDF} estimation.
        \emph{HN} and \emph{LN} indicate high or low neuroticism, respectively, and \emph{ExG fit} indicates a timing model which fits an \ac{exGaussian} distribution to the execution time data for each step.
    }\label{fig:samples}
\end{figure}

The results of this investigation are presented in \cref{fig:samples}
They clearly show the potentially dramatic effects of more accurate execution time estimation when optimizing sampling rates.
When using the realistic model for execution time estimation, the sampling schemes achieve between \SI{22}{\percent} and \textasciitilde\SI{25}{\percent} better average performance.
This is true even for configurations with low neuroticism which do not exactly match the parameterization of the external timing model driving the execution times for the steps, showing thus the importance of even less-accurate approximations.

>>>>

\begin{figure}
    \centering
    \begin{subfigure}[]{\columnwidth}
        \centering
        \includegraphics[width=\textwidth]{figs/new_model/lifetime_all_ttfs.png}
        \caption{%
            Evolution of mean application lifetimes as \acp{TTF} increase.
            Error bars indicate \SI{95}{\percent} \acp{CI}.
        }
    \end{subfigure}
    \begin{subfigure}[]{\columnwidth}
        \centering
        \includegraphics[width=\textwidth]{figs/new_model/lifetime_diff.png}
        \caption{%
            Percentage difference in mean application lifetimes with respect to the reference model at select \acp{TTF}.
            Error bars indicate the \SI{95}{\percent} \acp{CI}, calculated using a two-sided T-test.
        }
    \end{subfigure}
    \caption{\acl{TTF} versus application lifetime.}\label{fig:lifetimes}
\end{figure}

@@

We proceed to set up an experiment where these sampling scheme variants are deployed on identical, simulated, \num{100}-step tasks.
Also included for reference in this experiment is greedy (also known as \emph{zero-wait}) sampling, where samples are taken as fast as possible; a new sample is taken as soon as the result for the previous one has been received.
This is the default sampling strategy used in most existing \ac{WCA} prototypes.
The execution times for each step are generated by a realistic model parameterized with high neuroticism and without any distribution fitting on the data (this timing model is separate from the internal timing models inside the sampling schemes).
We set \( R_\text{min} \) to \SI{0.5}{\hertz} and \( \alpha \) to \num{3.0}.
The \ac{RTT} of the system is set to one of \SIlist[list-final-separator={, or}]{150;300;600}{\milli\second}, constant for all steps of the task.
For each combination of sampling scheme configuration (original adaptive by \textcite{Wang2019Towards}, adaptive with \edgedroid{} model, greedy) and \ac{RTT}, we run \num{100} repetitions of the task for good statistical significance.

\begin{figure*}
    \centering
    \begin{subtable}[t]{.3\textwidth}
        \centering
        \caption{Parameters used for \textcite{Wang2019Towards}'s adaptive sampling scheme.}
        \medskip
        \begin{tabular}{lr}
            \toprule
            \( R_\text{min} \)  & \SI{0.5}{\hertz} \\
            \( \alpha \)        & \num{3.0} \\
            \ac{RTT}            & \SIlist{150;300;600}{\milli\second} \\
            \bottomrule
        \end{tabular}
    \end{subtable}%
    \hspace{.05\textwidth}%
    % \begin{subfigure}[]{\columnwidth}
    %     \centering
    %     \includegraphics[width=\textwidth]{figs/new_model/sampling_junjue.png}
    %     \caption{%
    %         Mean number of samples per step over a \num{100}-step task, \num{90} independent repetitions per configuration.
    %         Error bars indicate \SI{95}{\percent} \acp{CI}.
    %     }
    % \end{subfigure}
    \begin{subtable}[t]{.6\textwidth}
        \centering
        \caption{Mean number of captured samples per sampling scheme at the three different \acp{RTT}.}
        \medskip
        \begin{tabular}{lrrr}
            \toprule
            Sampling scheme & \SI{150}{\milli\second} & \SI{300}{\milli\second} & \SI{600}{\milli\second} \\
            \midrule
            Adaptive (ED2 LN) & \num{14.69} & \num{8.07} & \num{5.10} \\
            Adaptive (ED2 HN) & \num{14.60} & \num{8.03} & \num{5.05} \\
            Adaptive (ED2 LN, ExG fit) & \num{15.30} & \num{8.23} & \num{5.09} \\
            Adaptive (ED2 HN, ExG fit) & \num{15.05} & \num{8.47} & \num{5.20} \\
            Adaptive (reference, gaussian fit) & \num{20.17} & \num{10.65} & \num{6.04} \\
            Greedy & \num{36.68} & \num{19.11} & \num{10.36} \\
            \bottomrule
        \end{tabular}
    \end{subtable}\\
    \bigskip
    \begin{subfigure}[]{\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{figs/new_model/diff_sampling_junjue.png}
        \caption{%
            Percentage reduction in mean number of captured samples per step (higher is better).
            Error bars indicate the \SI{95}{\percent} \acp{CI}, calculated using a two-sided T-test.
            % \todo[inline]{%
            %     Add greedy.
            %     Develop optimal sampling scheme?
            %     Explain grouping better?
            % }
        }
    \end{subfigure}
    \caption{%
        Results of parameterizing \textcite{Wang2019Towards}'s adaptive sampling scheme using the realistic timing model.
        \emph{ED2} indicates a sampling scheme using the \edgedroid{} model for \ac{CDF} estimation.
        \emph{HN} and \emph{LN} indicate high or low neuroticism, respectively, and \emph{ExG fit} indicates a timing model which fits an \ac{exGaussian} distribution to the execution time data for each step.
    }\label{fig:samples}
\end{figure*}

The results of this investigation are presented in \cref{fig:samples}
They clearly show the potentially dramatic effects of more accurate execution time estimation when optimizing sampling rates.
When using the realistic model for execution time estimation, the sampling schemes achieve between \SI{14}{\percent} and \textasciitilde\SI{27}{\percent} better average performance, depending on the \edgedroid{} model parameterization and the system \ac{RTT}.
\todo[inline]{Discuss that lower RTTs lead to better results?}
This is true even for configurations with low neuroticism which do not exactly match the parameterization of the external timing model driving the execution times for the steps, showing thus the importance of even less-accurate approximations.
